Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-13 TACAS2018/paper.tex
Moved jury's criterion to the appendix

There are a number of algorithms that can be
used for stability analysis~\cite{daes20161,Bessa16}.
Since the canonical forms used in this work use the coefficients of the
characteristic polynomial $S(z)$ as opposed to its roots (which are
extremely hard to calculate for a SAT solver), we choose Jury's
criterion~\cite{astrom1997computer} to check the stability in the
$z$-domain in view of its efficiency.

@@

@@

The CEGIS loop for this approach

@@

>>>>

In this work we are interested in asymptotic stability: asymptotic
stability is a property that amounts to convergence of the model
executions to an equilibrium point, starting from any states in a
neighborhood of the point.

%% There are a number of algorithms that can be
%% used for stability analysis~\cite{daes20161,Bessa16}.

A discrete-time LTI system is
asymptotically stable if all the roots of its characteristic
polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
K$) are inside the unity circle of the complex plane, i.e., their
absolute values are strictly less than one~\cite{astrom1997computer}
(this simple sufficient condition can be generalised, however this is
not necessary in our work).  In this paper, we express this stability
specification $\phi_\mathit{stability}$ in terms of a check known as
\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
formula to select the entries of matrix $K$ so that the closed-loop
dynamics are shaped as desired.

@@

\todo{this descrition does not mention two synthesis phases, which we should
focus on more.}

@@

The CEGIS loop for this approach 
\todo{the description here is incomplete (stops at phase 4).}

@@

%-------------------------------
\section{Stability} 
\label{ssec:stabspecification}
%-------------------------------

There are a number of algorithms that can be
used for stability analysis~\cite{daes20161,Bessa16}.

A discrete-time LTI system as \eqref{eq:closedloopss} is
asymptotically stable if all the roots of its characteristic
polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
K$) are inside the unity circle of the complex plane, i.e., their
absolute values are strictly less than one~\cite{astrom1997computer}
(this simple sufficient condition can be generalised, however this is
not necessary in our work).  In this paper, we express this stability
specification $\phi_\mathit{stability}$ in terms of a check known as
\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
formula to select the entries of matrix $K$ so that the closed-loop
dynamics are shaped as desired.

Since the canonical forms used in this work use the coefficients of the
characteristic polynomial $S(z)$ as opposed to its roots (which are
extremely hard to calculate for a SAT solver), we choose Jury's
criterion~\cite{astrom1997computer} to check the stability in the
$z$-domain in view of its efficiency.
